Hyper-linked Communications: WebRTC enabled asynchronous collaboration

### 2016-03-15 tese1/09_related_work_signaling.tex
[ADD] organizing arch

  \ac{XMPP} was initially developed for instant messaging and presence (Jabber\footnote{\url{http://jabber.org/}(accessed June 1, 2015).}). It is nowadays an open technology for standardized, decentralized, secure and extensible real-time communications. 
  \ac{XMPP} messages are \ac{XML} based, which is attractive for applications that need structured messages and rich hypermedia. Another advantage of \ac{XMPP} is the addition of extensions, for example \cite{xep0096}, which adds file transfer capabilities between two entities and \cite{xep0045} which enables multi-user chat.
  \ac{XMPP}'s bi-directional communication over \ac{HTTP} is achieved through \ac{BOSH} \cite{xep0206}.
  %RP falta um `` bi-directional communication OVER HTTP is achieved through''?
  %RP BOSH já foi explicado antes pelo que não vale a pena voltar a falar em long-pooling
  This kind of communication is also possible through WebSockets \cite{rfc7395}.
  Today, multiple XMPP server implementations exists, such as: \emph{ejabberd}\footnote{\url{http://jabberd.im/}(accessed June 1, 2015).}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}(accessed June 1, 2015).}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}(accessed June 1, 2015).} and \emph{Prosody}\footnote{\url{http://prosody.im/}(accessed June 1, 2015).}. \emph{Ejabberd} is the server that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}(accessed June 1, 2015).}.
  %RP fazes muitos paragrafos. Um paragrafo por tecnologia é normalmente suficiente se não forem muito grandes.

>>>>

  \ac{XMPP} was initially developed for instant messaging and presence (Jabber\footnote{\url{http://jabber.org/}(accessed June 1, 2015).}). It is nowadays an open technology for standardized, decentralized, secure and extensible real-time communications. 
  \ac{XMPP} messages are \ac{XML} based, which is attractive for applications that need structured messages and rich hypermedia. Another advantage of \ac{XMPP} is the addition of extensions, for example \cite{xep0096}, which adds file transfer capabilities between two entities and \cite{xep0045} which enables multi-user chat.
  \ac{XMPP}'s bi-directional communication over \ac{HTTP} is achieved through \ac{BOSH} \cite{xep0206}.
  %RP falta um `` bi-directional communication OVER HTTP is achieved through''?
  %RP BOSH já foi explicado antes pelo que não vale a pena voltar a falar em long-pooling
  This kind of communication is also possible through WebSockets \cite{rfc7395}.
  Today, multiple \ac{XMPP} server implementations exists, such as: \emph{ejabberd}\footnote{\url{http://jabberd.im/}(accessed June 1, 2015).}, \emph{Metronome}\footnote{\url{http://lightwitch.org/metronome}(accessed June 1, 2015).}, \emph{Openfire}\footnote{\url{http://igniterealtime.org/projects/openfire/}(accessed June 1, 2015).} and \emph{Prosody}\footnote{\url{http://prosody.im/}(accessed June 1, 2015).}. \emph{Ejabberd} is the server that implements more \ac{RFC} specifications and \ac{XEP}s\footnote{\url{http://en.wikipedia.org/wiki/Comparison_of_XMPP_server_software}(accessed June 1, 2015).}.
  %RP fazes muitos paragrafos. Um paragrafo por tecnologia é normalmente suficiente se não forem muito grandes.

{\color{blue}

    One of the advantages that \ac{XMPP} based applications offer is the possibility to send messages across different servers, an \ac{XMPP} user is identified by its \textit{Jabber ID} which is definined by the pair username and server name in the form \textit{username@server}.

    The user profile is represented in terms of Data Forms\cite{xep0004} protocol and managed (registration and update) through \textit{Info/Query} (IQ) \cite{rfc3920} requests to the \ac{XMPP} server which responds with an IQ response containing information to retrieve the registration fields needed to fill its profile (eg username, password, telephone).

    An important aspect of this model is the ability to define a user as a set of attributes that can change dinamically in order to fit the IM applications needs.

    The connection to the \ac{XMPP} server can be done through the same web server as the user is connected, but this web server would handle a lot of connections and that would have a great impact on the overall system performance.

    Typically a web application consists in multiple web pages which are navigated by users. Each time a webpage is accessed, either from a new context or a transition from a previous page, its context is cleared except for local storage and cookies, the javascript context is cleared, including the \ac{XMPP} connections performed by \emph{strophe.js}, an automatic mechanism is required for avoiding the user implicit reauthentication.

    One solution for reauthentication can be achieved by storing the user's JabberID and password on local storage and everytime a page is accessed the authentication is performed without the users knlowledge. Clearly this solution represents security flaws, the local storage can be easily accessed (HOW? explain!) locally or by performing a cross site scripting attack and reveal all the local storage, the same problem arises if the credentials are stored on cookies.

    An alternative solution is known as Session Attachment \footnote{\url{https://metajack.im/2008/10/03/getting-attached-to-strophe/}}, which requires that a \textit{session identifier}(SID) together with a \textit{initial request identifier (RID)} is passed to strophe.js in order to re-connect to the same stream on \ac{XMPP} server. Either SID and RID are unpredictable and, particularly, \textit{RID} changes on every request which is worthless if a user mantains more than one tab opened, for example for multiple conversations at the same time.

    Another alternative would be the development of our solution in a single web page, which would increse drastically the complexity of our web application.

    We know that an \ac{XMPP} based application could simplify our work just by using functionalities that XMPP already implemment, but from all the \ac{XMPP} features, we don't need all of them, in fact we just need a subset of \ac{XMPP} features, namely a simple way to register users, access and edit user's information, create chat rooms, send messages and access to presence information.
}

### 2016-03-15 tese1/XX_implementation_signaling.tex
[ADD] organizing arch

Our signaling protocol consists in sending JSON formated messages over WebSockets

>>>>

Our signaling protocol consists in send and receiving JSON formated messages over WebSockets by both the server and client.

\begin{lstlisting}[caption={General structure of our WebSocket messages},language=json]
{
	"cmd":<cmd>,
	"data":<data>
}
\end{lstlisting}

When a user enters in a group conference, after the page is completely loaded it is created a WebSocket that mantains a connection with our web servers. 
Before creating the web socket, we must identify the user and check if he has permissions to participate in the conference. This is done by retrieving the session id from the cookie provided by the user through the \ac{HTTP} headers. It's important to save de user identification before the socket is created because after the the handshake performed by the \emph{WebSocket} protocol\cite{rfc6455} the \ac{HTTP} context is lost.

When the connection is established between the server and the client, a \emph{PeerConnection} is created on the client and imediately after an \ac{WebRTC} endpoint on the server specifying a possible set of \ac{ICE} servers to connect.

The user is asked if he whants to share its camera and microphone, share screen or just receive streams from the server. If the user decides to perform a screen share, \emph{adapter.js}\footnote{\url{https://github.com/Temasys/AdapterJS}(accessed March 15, 2015).} may ask to install a pluggin if the browser doesn't support screen sharing.

If the user decides to share either from camera of screen, \emph{getUserMedia} is called with the correspondent contraints in order to obtain a local stream.

\begin{lstlisting}[caption={Media constraints},language=JavaScript]
var screenShareConstraints = {	
	"video": {
		"mediaSource": "window" || "screen"
	}, 
	"audio": false
};
var cameraMicrophoneConstraints = {
	"audio":true, 
	"video":true 
};
var receiveOnlyConstraints = {
	"offerToReceiveAudio":true,
	"offerToReceiveVideo":true
};
\end{lstlisting}

A popup is raised in order to ask the user to give permission to share those resources. If the resources are shared successfully the user creates an offer, sets a \emph{local session description} to its \emph{PeerConnection} and sends it through WebSockets. If the resources are not shared or the user specified to receive stream only, an offer is created specifying the contraints for receiving only video and audio.

The server receive and processes the offer and sets the \emph{remote session description} to its client associated \ac{WebRTC} endpoint. Then a \emph{local session description} is created on the server and sent back to the client, after that the server trys to gather \ac{ICE} candidates.

The client receives the server answer, sets the \emph{remote session description} and gets the ice candidates from the \ac{ICE} server.

After a while both the server and client receive the \ac{ICE} candidates that allow the client to connect directly to \ac{KMS} and vice-versa. The candidates are received at the client which sets them to its \emph{PeerConnection}. The same is done on the server which receives the \ac{ICE} candidates from the client and propagates them to \ac{KMS}.

The media session is established, the server starts to record any received stream and the client created an \ac{URL} correspondent to the stream location.

\begin{figure}[H]
    \centering
    \begin{subfigure}[b]{\textwidth}
    	\includegraphics[width=\textwidth]{figures/signaling}
    \end{subfigure}
    \caption{Signaling sequence diagram}
\end{figure}
